DRAFT: Harmonized and trait aggregation paper

### 2020-11-11 Paper/Results/SI.tex
11.11: Paper Update text

\subsubsection*{Simulation of varying taxonomic hierarchies}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
    \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability. Boxplots depict results for each trait aggregation method of 100 simulations. T1 to T3 are the simulated traits.}
    \label{fig:overview_sim_results}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
    \caption{Comparison of the results of the trait aggregation methods for every simulated dataset. Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted. Only the comparisons are shown were differences greater than 0.1 occurred.}
    \label{fig:sim_indv_runs}
\end{figure}

@@

\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
\label{subsec:SI_szoecs_reanalysis}

\subsubsection*{RDA of trait composition}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
    \caption{RDA of traits constrained by electric conductivity using harmonized grouping features. Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the right indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al. \cite{szocs_effects_2014}.
    } 
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
    \caption{RDA of traits constrained by electric conductivity. Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the right indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled.
    } 
\end{figure}

\subsubsection*{Trait distribution along first RDA axis}

% ASK: 
% - there seems to be some overlap of text on the top left
% - Why mention life cylce duration separately?
\begin{figure}[H]
    \centering
    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
    \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
    } 
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
    \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
    .
    }
\end{figure}

\newpage
\subsubsection*{Linear models of trait proportions}

\textit{Linear models of trait proportions with harmonized traits:}
\begin{table}[ht]
    \centering
    \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year. Trait proportions were logit transformed prior model building, estimates are on the logit scale. Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically significant effects (p $<$ 0.05).}
    \label{stab:linear_models_new}
    \begin{tabular}{l|ccccc}
    \toprule[.1em]
    & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\ 
    \toprule[.1em]
    Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
    Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
    Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
    Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
    Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
    Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
    \bottomrule
    \end{tabular}
    \textit{* p.value = 0.055}
\end{table}
\newline
\newline
\newline
\textit{Linear models of trait proportions Szöcs et al. :}
\begin{table}[ht]
    \centering
    \caption{Results of linear models for the five selected traits for Szöcs et al. \cite{szocs_effects_2014}. Trait proportions were logit transformed prior model building, estimates are on the logit scale.
    Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
    significant effects (p $<$ 0.05).}
    \label{stab:linear_models_edi}
    \begin{tabular}{l|ccccc}
    \toprule[.1em]
    & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\ 
    \toprule[.1em]
    Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
    Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
    Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
    Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
    Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
    Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
    \bottomrule
    \end{tabular} 
\end{table}

\subsubsection*{Trait proportions over time}
\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
    \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
    } 
\end{figure}

% Trait proportions over time
\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
    \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
\end{figure}

>>>>

%\subsubsection*{Simulation of varying taxonomic hierarchies}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
%     \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability. Boxplots depict results for each trait aggregation method of 100 simulations. T1 to T3 are the simulated traits.}
%     \label{fig:overview_sim_results}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
%     \caption{Comparison of the results of the trait aggregation methods for every simulated dataset. Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted. Only the comparisons are shown were differences greater than 0.1 occurred.}
%     \label{fig:sim_indv_runs}
% \end{figure}

@@

%\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
%\label{subsec:SI_szoecs_reanalysis}

% \subsubsection*{RDA of trait composition}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
%     \caption{RDA of traits constrained by electric conductivity using harmonized grouping features. Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the right indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al. \cite{szocs_effects_2014}.
%     } 
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
%     \caption{RDA of traits constrained by electric conductivity. Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the right indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled.
%     } 
% \end{figure}

% Not sure if the next two sections are really needed
% Need also to run analysis again
%\subsubsection*{Trait distribution along first RDA axis}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
%     \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
%     } 
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
%     \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
%     .
%     }
% \end{figure}

\newpage
% \subsubsection*{Linear models of trait proportions}

% \textit{Linear models of trait proportions with harmonized traits:}
% \begin{table}[ht]
%     \centering
%     \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year. Trait proportions were logit transformed prior model building, estimates are on the logit scale. Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically significant effects (p $<$ 0.05).}
%     \label{stab:linear_models_new}
%     \begin{tabular}{l|ccccc}
%     \toprule[.1em]
%     & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\ 
%     \toprule[.1em]
%     Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
%     Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
%     Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
%     Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
%     Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
%     Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
%     \bottomrule
%     \end{tabular}
%     \textit{* p.value = 0.055}
% \end{table}
% \newline
% \newline
% \newline
% \textit{Linear models of trait proportions Szöcs et al. :}
% \begin{table}[ht]
%     \centering
%     \caption{Results of linear models for the five selected traits for Szöcs et al. \cite{szocs_effects_2014}. Trait proportions were logit transformed prior model building, estimates are on the logit scale.
%     Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
%     significant effects (p $<$ 0.05).}
%     \label{stab:linear_models_edi}
%     \begin{tabular}{l|ccccc}
%     \toprule[.1em]
%     & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\ 
%     \toprule[.1em]
%     Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
%     Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
%     Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
%     Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
%     Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
%     Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
%     \bottomrule
%     \end{tabular} 
% \end{table}

% \subsubsection*{Trait proportions over time}
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
%     \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
%     } 
% \end{figure}

% % Trait proportions over time
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
%     \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
% \end{figure}
